---
title: "Initial explore"
author: "Julianna Renzi"
date: "10/17/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# for multidimentional stuff
require(vegan)
require(RVAideMemoire)
require(goeveg) # stress plot

require(worms) # for taxonomic information using the World Registry of Marine Species

require(tidyverse)
require(here)



```

Initial explore


# Bring in data

```{r}
alldat <- read_csv(here("data/cafi_data_sheet_with_dropdown.csv"))
metadat <- read_csv(here("data/Coral_metadata.csv"))
```

How many unique taxa names did I use?

```{r}
alldat %>% 
  select(search_term) %>% 
  unique() %>% 
  arrange(search_term) -> taxa

dim(taxa)
```

Can we attach the wormsID to these values?

```{r}
# alcl <- wormsbymatchnames("Arete indicus")

#  taxa %>% 
#    # do it just for the taxa that have search term level data
#    filter(!is.na(search_term)) %>% 
#    rowwise() %>% 
#    mutate(Alphia_id = wormsbymatchnames(search_term)$AlphiaID) %>% 
#    mutate(Family = wormsbymatchnames(search_term)$family) %>% 
#    mutate(Status = wormsbymatchnames(search_term)$status) -> wormz
#  # this is really slow so can save it as a CSV and read in as needed

write_csv(wormz, here("data/worms.csv"))
wormz <- read_csv(here("data/worms.csv"))
```

Then make groupings for those we want at above family level. General groups are: hermit, worm, limpet, bivalve, amphipod, Tanaidacea. Think about adding in brittles?

```{r}
alldat %>% 
  select(-family) %>% # we want to make our own family
  left_join(wormz, by = "search_term") %>% 
  mutate(Taxa_group = case_when(type == "bivalve" ~ "Bivalve",
                                type == "hermit" ~ "Hermit",
                                type == "amphipod" ~ "Amphipod",
                                type == "limpet" ~ "Limpet",
                                type == "worm" ~ "Worm",
                                search_term == "Tanaidacea" ~ "Peracarid",
                                code == "HARA" ~ "Peracarid",
                                code == "OPEL" ~ "Brittle",
                                code == "BRDE" ~ "Brittle",
                                code == "OPSC" ~ "Brittle",
                                code == "OPER" ~ "Brittle",
                                code == "BRPI" ~ "Brittle",
                                code == "OPSE" ~ "Brittle",
                                code == "AMSQ" ~ "Brittle",
                                code == "MALO" ~ "Brittle",
                                code == "OPSA" ~ "Brittle",
                                code == "OPSP" ~ "Brittle",
                                search_term == "Ophiocoma" ~ "Brittle",
                                code == "OPPE" ~ "Brittle",
                                TRUE ~ Family)) %>% 
  # remove one unidentified snail (if the data change BE WARY OF THIS STEP)
  filter(!is.na(Taxa_group)) -> cafi_grouped

```

## Change Sm/Med/Lg to numeric

First look at distribution of data to get estimates for DAAR and DAFL size range

```{r}

cafi_grouped %>% 
  filter(cafi_size_mm != "Med" &
           cafi_size_mm != "XL" &
           cafi_size_mm != "Lg" &
           cafi_size_mm != "Sm") %>% 
  mutate(cafi_size_mm = as.numeric(cafi_size_mm)) -> fish_dist
```

Plot it/summarize for DAAR

```{r}
fish_dist %>% 
  filter(code == "DAAR") %>% 
  ggplot(aes(x = cafi_size_mm)) +
  geom_histogram()

fish_dist %>% 
  filter(code == "DAAR") %>% 
  select(cafi_size_mm) %>% summary() 
```

And for DAFL

```{r}
fish_dist %>% 
  filter(code == "DAFL") %>% 
  ggplot(aes(x = cafi_size_mm)) +
  geom_histogram()

fish_dist %>% 
  filter(code == "DAFL") %>% 
  select(cafi_size_mm) %>% summary() 
```

Let's set third quartile as large, max as extra large, mean as medium

```{r}
cafi_grouped %>% 
  mutate(cafi_size_mm = case_when(code == "DAFL" & cafi_size_mm == "Sm" ~ "18.50",
                                  code == "DAFL" & cafi_size_mm == "Med" ~ "31.17",
                                  code == "DAFL" & cafi_size_mm == "Lg" ~ "42.50",
                                  code == "DAFL" & cafi_size_mm == "XL" ~ "65.00",
                                  code == "DAAR" & cafi_size_mm == "Sm" ~ "7.00",
                                  code == "DAAR" & cafi_size_mm == "Med" ~ "10.69",
                                  TRUE ~ cafi_size_mm)) %>% 
  mutate(cafi_size_mm = as.numeric(cafi_size_mm)) -> cafi
```




# Explore

## COMOs

Start with the COMOs because they were of interest

```{r}
alldat %>% 
  filter(search_term == "Coralliophila monodonta") %>% 
  group_by(coral_id, cafi_size_mm) %>% 
  summarize(Abundance = sum(count)) %>% 
  ungroup() -> comos
```

Attach to metadata

First clean a little 

```{r}
metadat %>% 
  # decide to use 9_broken dimensions instead of unbroken
  mutate(Coral_ID = case_when(Coral_ID == "9_broken" ~ "9", 
                              TRUE ~ Coral_ID)) %>% 
  filter(Coral_ID != "9_unbroken") %>% 
  # make it a number
  mutate(Coral_ID = as.numeric(Coral_ID)) %>% 
  rename(coral_id = Coral_ID) %>% 
  # change coral 40 here
  mutate(Crab = case_when(coral_id == 40 ~ "N",
                          TRUE ~ Crab)) %>% 
  mutate(Treatment = case_when(coral_id == 40 ~ "Control",
                          TRUE ~ Treatment)) -> metadat9
```

```{r}
comos %>% 
  left_join(metadat9, by = c("coral_id")) %>% 
  # calculate volume
  mutate(Coral_vol = 4/3*pi*(0.5*Height_cm)*(0.5*Longest_length_cm)*(0.5*Perpendicular_to_longest_length_cm)) -> comos_size # McKeon et al. 2012 (Oecologia) calculated volume consumed as an ellipsoid (4/3ðœ‹ð‘Žð‘ð‘, where a is half the length, b is half the width, and c is half the depth)
```

Also get one for count

```{r}
comos_size %>% 
  group_by(coral_id, Block, Treatment, Crab, Nutrients, Coral_vol) %>% 
  summarize(Abundance = sum(Abundance)) -> comos_count
```


### Plot it

```{r}
comos_size %>% 
  ggplot(aes(x = as.integer(cafi_size_mm), fill = Treatment)) +
  geom_histogram(stat="count") +
  facet_wrap(.~Treatment) +
  theme_bw()

# versus..
comos_count %>% 
  ggplot(aes(x = Treatment, y = as.integer(Abundance), fill = Treatment)) +
  geom_boxplot() +
  theme_bw()



```

```{r}
comos_count %>% 
  ggplot(aes(x = Coral_vol), color = Treatment) +
  geom_density() +
  facet_wrap(.~Treatment) +
  theme_bw()
```


### Maybe stats?

Is there a difference in the volume of corals between treatments?

```{r}
lm.size <- lm(Coral_vol ~ Treatment, data = comos_count)
  summary(lm.size) # YAY!
```

Is there a difference in COMO abundance?

```{r}
m.como <- glm(Abundance ~ Crab + Nutrients + Coral_vol, family = poisson, data = comos_count)
  summary(m.como)
  
# if we change it so 40 is not crab
comos_count %>% 
  mutate(Crab = case_when(coral_id == 40 ~ "N",
                          TRUE ~ Crab)) -> tst

m.como <- glm(Abundance ~ Crab + Nutrients + Coral_vol, family = poisson, data = tst)
  summary(m.como)
```

## DAFLs

```{r}
cafi %>% 
  filter(search_term == "Dascyllus flavicaudus") %>% 
  group_by(coral_id, cafi_size_mm) %>% 
  summarize(Abundance = sum(count)) %>% 
  ungroup() -> dafls
```



Attach to metadata

```{r}
dafls %>% 
  left_join(metadat9, by = c("coral_id")) %>% 
  # calculate volume
  mutate(Coral_vol = 4/3*pi*(0.5*Height_cm)*(0.5*Longest_length_cm)*(0.5*Perpendicular_to_longest_length_cm)) -> dafls_size # McKeon et al. 2012 (Oecologia) calculated volume consumed as an ellipsoid (4/3ðœ‹ð‘Žð‘ð‘, where a is half the length, b is half the width, and c is half the depth)
```

Also get one for count

```{r}
dafls_size %>% 
  group_by(coral_id, Block, Treatment, Crab, Nutrients, Coral_vol) %>% 
  summarize(Abundance = sum(Abundance)) -> dafls_count
```


### Plot it

```{r}
dafls_size %>% 
  ggplot(aes(x = as.integer(cafi_size_mm), fill = Treatment)) +
  geom_histogram(stat="count") +
  facet_wrap(.~Treatment) +
  theme_bw()

# versus..
dafls_count %>% 
  ggplot(aes(x = Treatment, y = as.integer(Abundance), fill = Treatment)) +
  geom_boxplot() +
  theme_bw()



```

```{r}
dafls_count %>% 
  ggplot(aes(x = Coral_vol), color = Treatment) +
  geom_density() +
  facet_wrap(.~Treatment) +
  theme_bw()
```

### What about small DAFLs?

```{r}
hist(dafls_size$cafi_size_mm) # maybe like, under 3 cm?

dafls_size %>% 
  filter(cafi_size_mm <= 30) %>% 
  group_by(coral_id, Block, Treatment, Crab, Nutrients, Coral_vol) %>% 
  summarize(Wittle_abundance = sum(Abundance)) -> bb_dafls
```

```{r}
bb_dafls %>% 
  ggplot(aes(x = Treatment, y = Wittle_abundance, fill = Treatment)) +
  geom_boxplot() +
  theme_bw()
```



### Maybe stats?

Is there a difference in DAFL abundance?

```{r}
m.dafl <- glm(Abundance ~ Crab + Nutrients + Coral_vol, family = poisson, data = dafls_count)
  summary(m.dafl)
  
# if we change it so 40 is not crab
dafls_count %>% 
  mutate(Crab = case_when(coral_id == 40 ~ "N",
                          TRUE ~ Crab)) -> tst

m.dafl <- glm(Abundance ~ Crab + Nutrients + Coral_vol, family = poisson, data = tst)
  summary(m.dafl)

```

For lil guyz

```{r}
m.lil.dafl <- glm(Wittle_abundance ~ Crab + Nutrients + Coral_vol, family = poisson, data = bb_dafls)
  summary(m.lil.dafl) # hmmm interesting--crabs and nutrients are good and seem to be additive. Not sure I understand why. Size didn't seem to matter so much?


```

# Alpheidae


```{r}
cafi %>% 
  filter(Family == "Alpheidae") %>% 
  group_by(coral_id, cafi_size_mm) %>% 
  summarize(Abundance = sum(count)) %>% 
  ungroup() -> alpheids
```



Attach to metadata

```{r}
alpheids %>% 
  left_join(metadat9, by = c("coral_id")) %>% 
  # calculate volume
  mutate(Coral_vol = 4/3*pi*(0.5*Height_cm)*(0.5*Longest_length_cm)*(0.5*Perpendicular_to_longest_length_cm)) -> alpheids_size # McKeon et al. 2012 (Oecologia) calculated volume consumed as an ellipsoid (4/3ðœ‹ð‘Žð‘ð‘, where a is half the length, b is half the width, and c is half the depth)
```

Also get one for count

```{r}
alpheids_size %>% 
  group_by(coral_id, Block, Treatment, Crab, Nutrients, Coral_vol) %>% 
  summarize(Abundance = sum(Abundance)) -> alpheids_count
```


### Plot it

```{r}
alpheids_size %>% 
  ggplot(aes(x = as.integer(cafi_size_mm), fill = Treatment)) +
  geom_histogram(stat="count") +
  facet_wrap(.~Treatment) +
  theme_bw()

# versus..
alpheids_count %>% 
  ggplot(aes(x = Treatment, y = as.integer(Abundance), fill = Treatment)) +
  geom_boxplot() +
  theme_bw()



```

```{r}
alpheids_count %>% 
  ggplot(aes(x = Coral_vol), color = Treatment) +
  geom_density() +
  facet_wrap(.~Treatment) +
  theme_bw()
```

### Stats?

Is there a difference in Alpheid abundance?

```{r}
m.alpheid <- glm(Abundance ~ Crab + Nutrients + Nutrients:Crab + Coral_vol, family = poisson, data =  alpheids_count)
  summary(m.alpheid) # whuttt
  
# if we change it so 40 is not crab
alpheids_count %>% 
  mutate(Crab = case_when(coral_id == 40 ~ "N",
                          TRUE ~ Crab)) -> tst

m.alpheid <- glm(Abundance ~ Crab + Nutrients + Coral_vol + Crab:Nutrients, family = poisson, data = tst)
  summary(m.alpheid) # hmmm 40 was really influential here

```

# Try multidimensional approach

Making the NMDS: https://cougrstats.wordpress.com/2019/12/11/non-metric-multidimensional-scaling-nmds-in-r/

Testing differences: https://www.introranger.org/post/ord-groups-gradients/

Another options: https://jonlefcheck.net/2012/10/24/nmds-tutorial-in-r/comment-page-1/

## Make a species matrix

```{r}
cafi %>% 
  group_by(coral_id, Taxa_group) %>% 
  # get abundance per taxa and coral
  summarize(Abundance = sum(count)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = Taxa_group, values_from = Abundance) %>% 
  # replace NA's with zeros
  mutate_all(~replace(., is.na(.), 0)) -> spp_matrix_name

spp_matrix_name %>% 
  # get rid of ID column
  select(-coral_id) -> spp_matrix_wide # no coral_ID
```

What to do with rare species?

- "Addressing the removal of rare species in multivariate bioassessments: The impact of methodological choices" by Poos and Jackson (2012) suggests leaving in all rare spp
- Comments on this blog (https://jonlefcheck.net/2012/10/24/nmds-tutorial-in-r/comment-page-1/) made me think it's probably at least removing families that only appear in one coral head

```{r}
# see how many columns have just one occurence

#colSums(spp_matrix_wide != 0) > 1

spp_mat_rare <- spp_matrix_wide[, colSums(spp_matrix_wide != 0) >= 2] # at least 2 occurrences (5% of samples)

# spp_mat_rare <- spp_matrix_wide
  
```

# Calculate distance

```{r}
nmds_bdd <- metaMDS(comm = spp_mat_rare, # community matrix
                    k = 3, # chosen based on the scree plot
                    distance = "bray", # bray-curtis distance
                    try = 1500) # number of iterations
                    
```

See everything we can pull out:

```{r}
names(nmds_bdd)

nmds_bdd$ndim # number of axes created
nmds_bdd$converged # did it converge?
nmds_bdd$stress # what's the stress of the final solution
nmds_bdd$distance # type of distance
nmds_bdd$tries # number of random initial configuration tried
nmds_bdd$points # scores for each sample (coral)
nmds_bdd$species # scores for variables/species

# and can plot simply:
plot(nmds_bdd) # open black circles correspond to samples and red crosses indicate variables

```


# Plot NMDS

```{r}
# create a data frame of the scores from the individual sites.
# This data frame will contain x and y values for where sites are located.
data_scores <- as.data.frame(scores(nmds_bdd))
```

Now attached metadata

```{r}
data_scores <- cbind(data_scores, spp_matrix_name[,"coral_id"])

# add other data 
data_scores %>% 
  left_join(metadat9, by = "coral_id") -> data_scores
```

Add the scores for species data

```{r}
species_scores <- as.data.frame(scores(nmds_bdd, "species"))
```


Add a column equivalent to the row name

```{r}
species_scores$species <- rownames(species_scores)
```

Build the plot

```{r}
ggplot() +
  geom_point(data = data_scores, aes(x = NMDS1, y = NMDS2, 
                                     color = Treatment), size = 3) +
  annotate(geom = "label", x = -.1, y = .6, size = 10,
           label = paste("Stress: ", round(nmds_bdd$stress, digits = 3))) +
  theme_minimal() +
  theme(legend.position = "right",
        text = element_text(size = 24))
```


Or try this way: https://stats-uoa.github.io/BIOSCI220/multivariate-data-analysis.html

```{r}
# for corals
sample_scores <- as.data.frame(nmds_bdd$points)

# add metadata
sample_scores <- cbind(sample_scores, metadat9)
```

And for species:

```{r}
spp_scores <- as.data.frame(nmds_bdd$species)
spp_scores$Species <- rownames(spp_scores)
```

Then plot:

```{r}
ggplot() +
  # the data points for each sample using the scores created in metaMDS function
  geom_point(data = sample_scores, aes(x = MDS1, y = MDS2, 
                                     color = Treatment), size = 3) +
  # create more appropriate x and y axis labels 
  xlab("nMDS1") +
  ylab("nMDS2") +
  # what colours would we like?
  scale_color_manual(values = inferno(15)[c(3, 8, 16, 11)],
                     name = "Treatment") +
  # add stress label to the plot, indicating the label position
  #annotate(geom = "label", x = -1.75, y = 2.75, size = 6,
   #        label = paste("Stress: ", round(nmds_bdd$stress, digits = 3))) +
  theme_minimal() + # choosing a theme
  theme(legend.position = "right",
        text = element_text(size = 10)) # position and size of legend
```

# Scree/stress plot

```{r}
dimcheckMDS(spp_mat_rare, distance = "bray", k=6) # k is max dimensions and default is 6
```

Also do a Shepard diagram

```{r}
stressplot(nmds_bdd)
```

# 3D plot

```{r}
require(vegan3d) # need to also download xQuartz
```

Use ordiplot3d

```{r}
# sample scores data
data_scores_3d <-scores(nmds_bdd, display = "sites")

# variable scores data
species_scores_3d <-scores(nmds_bdd, display = "species")
```


```{r}
#static 3-D variable scores plot
out <- ordiplot3d(species_scores_3d, col = "red", ax.col= "black", pch = 18)
text(out$xyz.convert(species_scores_3d), rownames(species_scores_3d), pos=1)
```

Try rotatable version

```{r}
#rotatable 3-D sample scores plot with sample points
ordirgl(data_scores_3d, col = "red", type = "p", ax.col= "black", pch = 18)
# to change points to sample labels use type = "t"

#rotatable 3-D variable scores plot with variable labels
ordirgl(species_scores_3d, col = metadat9$Treatment, type = "t", ax.col= "black", pch = 18)
```


Or try with plotly

```{r}
require(plotly)

plot_ly(x = data_scores_3d[,1], 
        y = data_scores_3d[,2], 
        z = data_scores_3d[,3],
        type = "scatter3d",
        mode = "markers",
        color = metadat9$Treatment) # can drag this around
```

# Try anosim

```{r}
bc_dist <- vegdist(spp_mat_rare, method="bray") 

nut.ano <- anosim(bc_dist, metadat9$Nutrients)
  summary(nut.ano)
  plot(nut.ano) 
  
trt.ano <- anosim(bc_dist, metadat9$Treatment)
  summary(trt.ano)
  plot(trt.ano) 

```

## What about just with core CAFI?

What are the most common CAFI?

```{r}
cafi %>% 
  group_by(coral_id, Taxa_group) %>% 
  # get abundance per taxa and coral
  summarize(Abundance = sum(count)) %>% 
  ungroup() %>% 
  left_join(metadat9, by = "coral_id") %>% 
  ggplot(aes(x = Treatment, y = Abundance, fill = Taxa_group)) +
  geom_bar(stat = "identity") 
```


```{r}
cafi %>% 
  group_by(Taxa_group) %>% 
  # get abundance per taxa and coral
  summarize(Abundance = sum(count)) %>% 
  arrange(-Abundance) 


# seems like a cutoff of 50 is a good place to start
cafi %>% 
  group_by(Taxa_group) %>% 
  # get abundance per taxa and coral
  summarize(Abundance = sum(count)) %>% 
  arrange(-Abundance) %>% 
  filter(Abundance >= 50) -> abundant_cafi
```

```{r}
cafi %>% 
  group_by(coral_id, Taxa_group) %>% 
  # get abundance per taxa and coral
  summarize(Abundance = sum(count)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = Taxa_group, values_from = Abundance) %>% 
  # replace NA's with zeros
  mutate_all(~replace(., is.na(.), 0)) %>% 
  select(coral_id, abundant_cafi$Taxa_group) -> core_spp_matrix

core_spp_matrix %>% 
  # get rid of ID column
  select(-coral_id) -> core_spp_matrix_wide # no coral_ID
```


## Calculate distance

```{r}
nmds_core <- metaMDS(comm = core_spp_matrix_wide, # community matrix
                    k = 3, # chosen based on the scree plot
                    distance = "bray", # bray-curtis distance
                    try = 1500) # number of iterations
                    
```

See everything we can pull out:

```{r}
names(nmds_core)

nmds_core$ndim # number of axes created
nmds_core$converged # did it converge?
nmds_core$stress # what's the stress of the final solution
nmds_core$distance # type of distance
nmds_core$tries # number of random initial configuration tried
nmds_core$points # scores for each sample (coral)
nmds_core$species # scores for variables/species

# and can plot simply:
plot(nmds_core) # open black circles correspond to samples and red crosses indicate variables

```


# Plot NMDS

```{r}
# create a data frame of the scores from the individual sites.
# This data frame will contain x and y values for where sites are located.
data_scores <- as.data.frame(scores(nmds_core))
```

Now attached metadata

```{r}
data_scores <- cbind(data_scores, core_spp_matrix[,"coral_id"])

# add other data 
data_scores %>% 
  left_join(metadat9, by = "coral_id") -> data_scores
```

Add the scores for species data

```{r}
species_scores <- as.data.frame(scores(nmds_core, "species"))
```


Add a column equivalent to the row name

```{r}
species_scores$species <- rownames(species_scores)
```

Build the plot

```{r}
ggplot() +
  geom_point(data = data_scores, aes(x = NMDS1, y = NMDS2, 
                                     color = Treatment), size = 3) +
  annotate(geom = "label", x = -.1, y = .6, size = 10,
           label = paste("Stress: ", round(nmds_core$stress, digits = 3))) +
  theme_minimal() +
  theme(legend.position = "right",
        text = element_text(size = 24))
```


## Try anosim

```{r}
bc_dist <- vegdist(core_spp_matrix_wide, method="bray") 

nut.ano <- anosim(bc_dist, metadat9$Nutrients)
  summary(nut.ano)
  plot(nut.ano) 
  
crab.ano <- anosim(bc_dist, metadat9$Crab)
  summary(crab.ano)
  plot(crab.ano) 
    
trt.ano <- anosim(bc_dist, metadat9$Treatment)
  summary(trt.ano)
  plot(trt.ano)  # Not a huge difference I don't think?

```



# Look at diversity metrics


```{r}
shann.in <- diversity(spp_mat_rare, index = "shannon")
simp.in <- diversity(spp_mat_rare, index = "simpson")
invSimp.in <- diversity(spp_mat_rare, index = "invsimpson")

div.metrics <- cbind(shann.in, simp.in, invSimp.in, metadat9)
```

```{r}
# shannon
div.metrics %>% 
  ggplot(aes(x = Treatment, y = shann.in, color = Treatment)) +
  geom_boxplot() +
  theme_minimal()

# shannon-crab
div.metrics %>% 
  ggplot(aes(x = Crab, y = shann.in, color = Crab)) +
  geom_boxplot() +
  theme_minimal()

# simpson
div.metrics %>% 
  ggplot(aes(x = Treatment, y = simp.in, color = Treatment)) +
  geom_boxplot() +
  theme_minimal()

# inverse simpson
div.metrics %>% 
  ggplot(aes(x = Treatment, y = invSimp.in, color = Treatment)) +
  geom_boxplot() +
  theme_minimal()

```

Compare using the Hutcheson t-test ? https://www.dataanalytics.org.uk/comparing-diversity/
https://www.rdocumentation.org/packages/ecolTest/versions/0.0.1/topics/multiple_Hutcheson_t_test 

```{r}
require(ecolTest)

multiple_Hutcheson_t_test(t(spp_mat_rare)) # nope
```

What about like a Kruskal-Wallis test?

```{r}
kruskal.test(simp.in ~ Treatment, data = div.metrics)
```

Or just an ANOVA?

```{r}
div.aov <- aov(shann.in ~ Crab + Nutrients + Crab:Nutrients, data = div.metrics)
  summary(div.aov)
```


# Gravid-ness?

```{r}
cafi %>% 
  filter(Taxa_group == "Trapeziidae") %>% 
  # fill in missing gravid lines
  mutate(Gravid = case_when(is.na(Gravid) ~ "N",
                            TRUE ~ Gravid)) -> trapeziids
```


```{r}
trapeziids %>% 
  group_by(coral_id, cafi_size_mm, Gravid) %>% 
  summarize(Abundance = sum(count)) %>% 
  ungroup() -> trapeziids.G

trapeziids %>% 
  group_by(coral_id, cafi_size_mm) %>% 
  summarize(Abundance = sum(count)) %>% 
  ungroup() -> trapeziids.noG
```

PLot

```{r}
trapeziids.G %>% 
  left_join(metadat9, by = "coral_id") %>% 
  ggplot(aes(x = Nutrients, y = Abundance, color = Gravid)) +
  geom_violin() +
  geom_jitter() +
  theme_minimal()
```




Attach to metadata

```{r}
trapeziids.noG %>% 
  left_join(metadat9, by = c("coral_id")) %>% 
  # calculate volume
  mutate(Coral_vol = 4/3*pi*(0.5*Height_cm)*(0.5*Longest_length_cm)*(0.5*Perpendicular_to_longest_length_cm)) -> trapeziids_size # McKeon et al. 2012 (Oecologia) calculated volume consumed as an ellipsoid (4/3ðœ‹ð‘Žð‘ð‘, where a is half the length, b is half the width, and c is half the depth)
```

Also get one for count

```{r}
trapeziids_size %>% 
  group_by(coral_id, Block, Treatment, Crab, Nutrients, Coral_vol) %>% 
  summarize(Abundance = sum(Abundance)) -> trapeziids_count
```


### Plot it

```{r}
trapeziids_size %>% 
  ggplot(aes(x = as.integer(cafi_size_mm), fill = Treatment)) +
  geom_histogram(stat="count") +
  facet_wrap(.~Treatment) +
  theme_bw()

# versus..
trapeziids_count %>% 
  ggplot(aes(x = Treatment, y = as.integer(Abundance), fill = Treatment)) +
  geom_boxplot() +
  theme_bw()



```

```{r}
trapeziids_count %>% 
  ggplot(aes(x = Coral_vol), color = Treatment) +
  geom_density() +
  facet_wrap(.~Treatment) +
  theme_bw()
```

### Stats?

Is there a difference in Trapeziid abundance?

```{r}
m.trapeziid <- glm(Abundance ~ Crab + Nutrients + Coral_vol, family = poisson, data =  trapeziids_count)
  summary(m.trapeziid) # hmmm yes more on the nutrient corals..
  

```

