---
title: "Water nutrients"
author: "Julianna Renzi"
date: "2/7/2023"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(here)
require(tidyverse)
require(RColorBrewer)
```

This script plots the results from the water nutrient analysis

# Bring in the data

```{r}
waterNut <- read_csv(here("data/Water_nutrients.csv"))

metadat <- read_csv(here("data/Coral_metadata.csv")) %>% 
  mutate(Coral_ID = case_when(Coral_ID == "9_broken" ~ "9", TRUE ~ Coral_ID))
```

Join the two together

```{r}
waterNut %>% 
  # just want the samples (not the standards/etc.)
  filter(!is.na(Coral_ID)) %>% 
  mutate(Coral_ID = as.character(Coral_ID)) %>% 
  left_join(metadat, by = "Coral_ID") %>% 
  mutate(Time_point = as.factor(Time_point)) -> nutrients
```

# Plot 

## Nitrate and nitrite

```{r}
nutrients %>% 
  ggplot(aes(x = Time_point, y = NitriteNitrate)) +
  geom_boxplot(aes(color = Nutrients)) +
  scale_color_manual(values = brewer.pal(n = 2, name = "Dark2")) +
  #geom_point(aes(x = Time_point, y = NitriteNitrate, color = Nutrients)) +
  theme_bw() +
  xlab("Time point") +
  ylab("Nitrite + Nitrate (umol)")

ggsave(filename = here("figures/Nitratenitratewater.jpg"), height = 3.5, width = 4.5)
```

## Nitrate

```{r}
nutrients %>% 
  mutate(Nitrate = NitriteNitrate- Nitrite) %>% 
  ggplot(aes(x = Time_point, y = Nitrate)) +
  geom_boxplot(aes(color = Nutrients)) +
  scale_color_manual(values = brewer.pal(n = 2, name = "Dark2")) +
  #geom_point(aes(x = Time_point, y = NitriteNitrate, color = Nutrients)) +
  theme_bw() +
  xlab("Time point") +
  ylab("Nitrate (umol)")

ggsave(filename = here("figures/Nitratewater.jpg"), height = 3.5, width = 4.5)
```
 
Basically the same

## Ammonia

```{r}
nutrients %>% 
  ggplot(aes(x = Time_point, y = Ammonia)) +
  geom_boxplot(aes(color = Nutrients)) +
  scale_color_manual(values = brewer.pal(n = 2, name = "Dark2")) +
  #geom_point(aes(x = Time_point, y = NitriteNitrate, color = Nutrients)) +
  theme_bw() +
  xlab("Time point") +
  ylab("Ammonia (umol)")

ggsave(filename = here("figures/Ammoniawater.jpg"), height = 3.5, width = 4.5)
```


## Phosphate

```{r}
nutrients %>% 
  ggplot(aes(x = Time_point, y = Phosphate)) +
  geom_boxplot(aes(color = Nutrients)) +
  scale_color_manual(values = brewer.pal(n = 2, name = "Dark2")) +
  #geom_point(aes(x = Time_point, color = Nutrients)) +
  theme_bw() +
  xlab("Time point") +
  ylab("Phosphate (umol)")

ggsave(filename = here("figures/Phosphatewater.jpg"), height = 3.5, width = 4.5)
```


## Ammonia

```{r}
nutrients %>% 
  ggplot(aes(x = Time_point, y = Ammonia)) +
  geom_boxplot(aes(color = Nutrients)) +
  scale_color_manual(values = brewer.pal(n = 2, name = "Dark2")) +
  geom_point(aes(x = Time_point, color = Nutrients)) +
  theme_bw() +
  xlab("Time point") +
  ylab("Ammonia (umol)")

ggsave(filename = here("figures/Ammoniawater.jpg"), height = 3.5, width = 4.5)
```


# Stats

## Nitrite+Nitrate

```{r}
nnmod <- aov(NitriteNitrate ~ Nutrients + Time_point, data = nutrients)
  summary(nnmod) # yes it elevated, seems no difference for time point?

```

Gotta check assumptions, but if not met do this:

```{r}
nnmodKW <- kruskal.test(NitriteNitrate ~ Nutrients, data = nutrients)
  nnmodKW # still good for nutrients
```

Might be weird because time point should probably also be a thing?


## Ammonia

```{r}
ammod <- aov(Ammonia ~ Nutrients + Time_point, data = nutrients)
  summary(ammod) # Just time point..
  
# interaction tho?
ammglm <- glm(Ammonia ~ Nutrients + Time_point + Nutrients:Time_point, family = gaussian, data = nutrients)
  summary(ammglm) # no--really just time point
  plot(ammglm)

```

Gotta check assumptions, but if not met do this:

```{r}
ammodKW <- kruskal.test(Ammonia ~ Nutrients, data = nutrients)
  ammodKW # nothing here
```


## Phosphate

```{r}
phosmod <- aov(Phosphate ~ Nutrients + Time_point, data = nutrients)
  summary(phosmod) # Just time point again
  
  
# interaction tho?
phosglm <- glm(Phosphate ~ Nutrients + Time_point + Nutrients:Time_point, family = gaussian, data = nutrients)
  summary(phosglm)
  plot(phosglm)

```

Gotta check assumptions, but if not met do this:

```{r}
ammodKW <- kruskal.test(Ammonia ~ Nutrients, data = nutrients)
  ammodKW # nothing here
```





